Multi-EWAS enrichment example

### 2024-01-16 figs/multi_ewas_example.Rmd
bugfix

r2 <- lapply(r2,function(r) {
  ups <- head(subset(r,p.adjustANOVA<0.05 & s.dist > 0.3)$set,5)
  dns <- head(subset(r,p.adjustANOVA<0.05 & s.dist < -0.3)$set,5)
  list("ups"=ups,"dns"=dns)
} )

>>>>

r2 <- lapply(r1,function(r) {
  ups <- head(subset(r,p.adjustANOVA<0.05 & s.dist > 0.3)$set,5)
  dns <- head(subset(r,p.adjustANOVA<0.05 & s.dist < -0.3)$set,5)
  list("ups"=ups,"dns"=dns)
} )
